---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# betacode

<!-- badges: start -->
[![R-CMD-check](https://github.com/xmarquez/betacode/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/xmarquez/betacode/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This package does exactly one thing: convert [beta code](https://en.wikipedia.org/wiki/Beta_Code) to unicode Greek text.

## Installation

You can install the development version of betacode from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("xmarquez/betacode")
```

## Examples

Here's a simple example of converting beta code to unicode:

```{r example}
library(betacode)
betacode_to_unicode("*sidw\\n e)pi\\ qala/tth| po/lis *)assuri/wn")
```

The package also includes the beta code from Plato's Republic (split into sentences, and sourced from the [Diorisis ancient Greek corpus](https://figshare.com/articles/dataset/The_Diorisis_Ancient_Greek_Corpus/6187256)), which one can use to test the package:

```{r example2}
library(dplyr)
plato_republic %>%
  slice_head(n = 10) %>%
  mutate(unicode_text = betacode_to_unicode(text)) %>%
  knitr::kable()
```

The package gives a warning when it encounters malformed beta code, but will produce output regardless. 

```{r}
betacode_to_unicode("*sidw\\n e)pi\\ qala/tth| po/lis a*)ssuri/wn")
```
However, it is possible to avoid some warnings by relaxing the matching order of accents and other diacritics by specifying `strict = FALSE`:

```{r}
betacode_to_unicode("fh|\\s")
betacode_to_unicode("fh|\\s", strict = FALSE)
```

